\LARGE \bf Reactive Trajectory Planning and Tracking Control for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-22 root.tex
fixing RSTOP diagrams
finished updating RSTOP/PSTOP pics

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{
    Segmentation of the path by path manager.
    The trajectory generation is serially called on each segment colored differently.
    \textbf{Need to update figure with stop signs???? ??????? ?????}
  }
  \label{fig:segmentation}
\end{figure}

@@

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}}
  \caption{Reactive behavior to pedestrian}
  \label{fig:react}
\end{figure}
\emph{RG: a figure text etc is smaller than b and c. maybe crop from right to make same size}

>>>>

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{
    Segmentation of the path by path manager.
    The trajectory generation is serially called on each segment colored differently.
  }
  \label{fig:segmentation}
\end{figure}

@@

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_Replan.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_Resume.png}}
  \caption{Reactive behavior to pedestrian}
  \label{fig:react}
\end{figure}
\emph{RG: a figure text etc is smaller than b and c. maybe crop from right to make same size}
